---
title: "R Exercise Session 8"
author: "Elizabeth Furth"
date: "6/28/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

First, clone the [Assignment8][1] repository to your own GitHub account
by forking. Look for the forking button on the GitHub repository page.

You can then modify the repository (namely the `R_Exercises8.Rmd` file)
and complete the assignment by adding your answers in the appropriate
place. Do **NOT** rename the file.

## Completing the assignment

Check your work by knitting the document.

1. Create a level 2 header below in Markdown with the name "Answer 1".

## Answer 1

2. Add an unordered Markdown list of your favorite food dishes and
add their ingredients as sub-items in the list. You should enter at least two
dishes with two ingredients each.

* Guacamole
  * Avocado
  * Tomato
  * Lemon juice
  * Salt
  * Pepper
* Ice Cream
  * Sugar
  * Salt
  * Cream
  * Ice
  * Chocolate
 
3. Insert an R code chunk below. Show the `summary` of the `Orange` dataset.
Run a linear regression using the `lm` function to predict `circumference` from
`age` and assign the result. Show the `summary` of the fit object that you
assigned.
```{r}
summary(Orange)
fit <- lm(circumference ~ age, data = Orange)
summary (fit)

```
 Tree       age         circumference  
 3:7   Min.   : 118.0   Min.   : 30.0  
 1:7   1st Qu.: 484.0   1st Qu.: 65.5  
 5:7   Median :1004.0   Median :115.0  
 2:7   Mean   : 922.1   Mean   :115.9  
 4:7   3rd Qu.:1372.0   3rd Qu.:161.5  
       Max.   :1582.0   Max.   :214.0  

Call:
lm(formula = circumference ~ age, data = Orange)

Residuals:
    Min      1Q  Median      3Q     Max 
-46.310 -14.946  -0.076  19.697  45.111 

Coefficients:
             Estimate Std. Error t value Pr(>|t|)    
(Intercept) 17.399650   8.622660   2.018   0.0518 .  
age          0.106770   0.008277  12.900 1.93e-14 ***
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

Residual standard error: 23.74 on 33 degrees of freedom
Multiple R-squared:  0.8345,	Adjusted R-squared:  0.8295 
F-statistic: 166.4 on 1 and 33 DF,  p-value: 1.931e-14

4. Add an RMarkdown weblink (in link format) below to your favorite R reference
website.

[Tutorials Point](https://www.tutorialspoint.com/r/index.htm)

5. Replace the author field in the `yaml` header with your name and then
successfully `knit` the RMarkdown document into a Word document.


6. Follow the [Pull Request instructions on GitHub](https://help.github.com/en/github/collaborating-with-issues-and-pull-requests/creating-a-pull-request-from-a-fork)
to submit your assignment via GitHub as a Pull Request to the [Assignment8][1]
repository.

[1]: https://github.com/CUNYSPHCode/Assignment8

